More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-09-20 2016-Weak-FH-Bisim/WeakBisim.tex
WT1, WT2, WT3

\title{More equivalences for Open pNets\thanks{This work was partially 
funded by the Associated Team FM4CPS
  between INRIA and ECNU, Shanghai}}
\author{ Ludovic Henrio\inst{1}  \ \ \  Eric Madelaine\inst{1,2} \ \ \ Rab\'ea}
\institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
	\and INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France
}
\date{}                                           % Activate to display a given date or no date

@@

\begin{definition}[Building a weak open automaton]\label{def:buildweakOT}
  Let $A = <J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton. 
The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,\WT>$ where $\WT$ is derived from $\mathcal{T}$ as follows

%\noindent{\bf Invisible $\tau$ transitions:}
\begin{mathpar}
 \openrule
         {
           \emptyset,\symb{True},Id(s)}
         {s \OTWeakarrow {\tau} s} \in \WT
 \end{mathpar}
and
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
}
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
%\inferrule{
% \openrule
%         {
%           \overline{\beta},\Pred,\Post}
%         {s \OTarrow {\tau} s'} \in \mathcal{T}
%\\
% \openrule
%         {
%           \overline{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
%         {s' \OTWeakarrow {\tau} s''} \in \WT
%}
%{ \openrule
%         {
%           \vis{\overline{\beta}}\dotcup\overline{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
%				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
%         {s \OTWeakarrow {\tau} s''} \in \WT
%}
 \end{mathpar}
and
%\noindent{\bf Other transitions:}
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in \WT
\qquad
\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
\qquad
\openrule
         {
           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
         {s_2 \OTWeakarrow {\tau} s'} \in\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
           \overline{\gamma_1}\dotcup \overline{\gamma_2}\dotcup\overline{\gamma_3},
		\Pred,
				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{mathpar}

>>>>

\title{More equivalences for Open pNets\thanks{This work was partially 
funded by the Associated Team FM4CPS
  between INRIA and ECNU, Shanghai}}
\author{Ludovic Henrio\inst{1}  \ \ \  Eric Madelaine\inst{1,2} \ \ \ Rab\'ea}
\institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
	\and INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France
}
\date{}                                           % Activate to display a given date or no date

@@

\begin{definition}[Building a weak open automaton]\label{def:buildweakOT}
  Let $A = <J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton. 
The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,\WT>$ where $\WT$ is derived from $\mathcal{T}$ as follows:

%\noindent{\bf Invisible $\tau$ transitions:}
\begin{mathpar}
 \openrule
         {
           \emptyset,\symb{True},Id(s)}
         {s \OTWeakarrow {\tau} s} \in \WT  \qquad \WTUn
 \end{mathpar}
and
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
} 
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}\qquad \WTDeux
%\inferrule{
% \openrule
%         {
%           \overline{\beta},\Pred,\Post}
%         {s \OTarrow {\tau} s'} \in \mathcal{T}
%\\
% \openrule
%         {
%           \overline{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
%         {s' \OTWeakarrow {\tau} s''} \in \WT
%}
%{ \openrule
%         {
%           \vis{\overline{\beta}}\dotcup\overline{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
%				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
%         {s \OTWeakarrow {\tau} s''} \in \WT
%}
 \end{mathpar}
 and
%\noindent{\bf Other transitions:}
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in \WT
\qquad
\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
\qquad
\openrule
         {
           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
         {s_2 \OTWeakarrow {\tau} s'} \in\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
           \overline{\gamma_1}\dotcup \overline{\gamma_2}\dotcup\overline{\gamma_3},
		\Pred,
				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha} s'} \in\WT
} \WTTrois
\end{mathpar}
